Generating and modifying matrices

### 2017-07-25 Analysis/Character_difference/Modifying_matrices.Rmd
Updated modifying matrix script to fit with the new version of dispRity

```{r, eval = FALSE}
## The latest version of devtools
if(!require(devtools)) install.packages("devtools")

## The latest version of dispRity 
install_github("TGuillerme/dispRity")

## The latest version of Claddis
install_github("graemetlloyd/Claddis")

@@

```{r, results="hide", message=FALSE}
library(Claddis) ; library(dispRity) ; library(diversitree)
source("functions.R") ; load.functions(test = FALSE)

## Load the C libraries
dyn.load("../Functions/char.diff.so")

@@

```{r, fig.width=12, fig.height=6}
par(mfrow = c(1, 2))
## The character difference density (per character)
plot.char.diff.density(char.diff(matrix_norm), "Normal matrix")
## The character difference matrix (pairwise)
plot.cor.matrix(char.diff(matrix_norm), main = "")
```

```{r, fig.width=12, fig.height=6}
par(mfrow = c(1, 2))
## The character difference density (per character)
plot.char.diff.density(char.diff(matrix_maxi), "Maximised matrix")
## The character difference matrix (pairwise)
plot.cor.matrix(char.diff(matrix_maxi), main = "")
```

```{r, fig.width=12, fig.height=6}
par(mfrow = c(1, 2))
## The character difference density (per character)
plot.char.diff.density(char.diff(matrix_mini), "Minimised matrix")
## The character difference matrix (pairwise)
plot.cor.matrix(char.diff(matrix_mini), main = "")
```

```{r, fig.width=12, fig.height=6}
par(mfrow = c(1, 2))
## The character difference density (per character)
plot.char.diff.density(char.diff(matrix_rand), "Randomised matrix")
## The character difference matrix (pairwise)
plot.cor.matrix(char.diff(matrix_rand), main = "")
```

>>>>

```{r, eval = TRUE}
## The latest version of devtools
if(!require(devtools)) install.packages("devtools")

## The latest version of dispRity 
if(!require(dispRity)) install_github("TGuillerme/dispRity")

@@

```{r, results="hide", message=FALSE}
## Loading the functions not included in dispRity
source("../../Functions/modify.matrix.R")

@@

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_norm <- char.diff(matrix_norm)
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_norm, type = "density", main = "Normal matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_norm, type = "matrix")
```

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_maxi <- char.diff(matrix_maxi)
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_maxi, type = "density", main = "Maximised matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_maxi, type = "matrix")
```

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_mini <- char.diff(matrix_mini)
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_mini, type = "density", main = "Minimised matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_mini, type = "matrix")
```

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_rand <- char.diff(matrix_rand)
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_rand, type = "density", main = "Randomised matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_rand, type = "matrix")
```

<!-- Paper figure -->

<!-- ```{r, fig.width=12, fig.height=12}
par(mfrow = c(2, 3), bty = "n", mar = c(1,1,1,1))
## Tree
plot(tree, cex = 0.8, main = "A - Simulated tree")
## Normal matrix
plot(char_diff_matrix_norm, type = "matrix", main = "B - Normal matrix", legend = FALSE)
## Empty plot
plot(0,0, col = "white", xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
## Maximised matrix
plot(char_diff_matrix_maxi, type = "matrix", main = "C - Maximised matrix", legend = FALSE)
## Minimised matrix
plot(char_diff_matrix_mini, type = "matrix", main = "D - Minimised matrix", legend = FALSE)
## Randomised matrix
plot(char_diff_matrix_rand, type = "matrix", main = "E - Randomised matrix", legend = FALSE)
```
 -->
